---
title: "Introduction To Substances."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction To Substances.}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(substances)
```

## Introduction

The `substances` package enables substance-aware unit conversions in R, allowing transformations between mass and molar units, as well as handling nonstandard medical unit conversions. It extends the functionality of the `units` package by incorporating molecular weight and domain-specific unit conversions.

## Installation

```{r}
devtools::install_github("https://github.com/geeky33/substances", build_vignettes = TRUE) 

```

## Creating Substances

The package defines a `substances` class with relevant properties such as name, molecular weight, and unit.

```{r}
library(substances)

# Creating a new substance
water <- new("substances", name = "water", molecular_weight = 18.02, unit = "g/mol")
```

## Mass-to-Molar Conversions

The package provides functions to convert between mass and moles for a given substance.

```{r}
# Convert 36.04 grams of water to moles
mass_to_moles(36.04, water)  # Output: 2 moles

# Convert 2 moles of water to mass
moles_to_mass(2, water)  # Output: 36.04 grams
```

## Medical Unit Conversions

The package supports conversions between nonstandard medical units.

```{r}
# Convert 50 U/L to ukat/L
convert_medical_units(50, "U/L", "ukat/L")  # Output: 5e-5 ukat/L
```

## Arithmetic Operations on Substances

The package supports basic arithmetic operations on substances.

```{r}
# Adding two identical substances
ethanol <- new("substances", name = "ethanol", molecular_weight = 46.07, unit = "g/mol")
combined_ethanol <- ethanol + ethanol
combined_ethanol@molecular_weight  # Output: 92.14 g/mol

# Scaling a substance
scaled_ethanol <- ethanol * 2
scaled_ethanol@molecular_weight  # Output: 92.14 g/mol
```

